NOTE: This code was heavily borrowed (HEAVILY BORROWED) from http://joshuamccrain.com/tutorials/maps/streets_tutorial.html.

I encountered this tutorial in my early stages in R, while looking for a package for creating
interactive maps for a class project at Nashville Software School (Leaflet was obviously the correct
solution, but like I said - it was very early stages in R).

While I didn't end up using this product in my final project, I always wanted an excuse to use it
because I love the clean, beautiful lines of the map. 

If you want to make a map for your own city, it should be a very simple process to replicate. 
For a more detailed tutorial, definitely check out Joshua's website. And if you want to see my
final project, a study of growing traffic in Tennessee, visit the link below!

https://matttparker.shinyapps.io/TnTraffic/


```{r}
library(tidyverse)
library(osmdata) # package for working with streets
library(showtext) # for custom fonts
library(ggmap)
library(rvest)
```

```{r}
# Find coordinate borders of your city
getbb("Nashville Tennessee")
```

```{r}
# Open streets has many categories of roads, so we'll start by combining them into just a few levels.
# These levels will be displayed by different thickness on the final product.
# Start with the largest roads. Use osmdata_sf() to convert them to a form which ggmap can read.
big_streets <- getbb("Nashville Tennessee")%>%
  opq()%>%
  add_osm_feature(key = "highway", 
                  value = c("motorway", "primary", "motorway_link", "primary_link")) %>%
  osmdata_sf()
```

```{r}
# Continue the same process, with two more levels of streets.
med_streets <- getbb("Nashville Tennessee")%>%
  opq()%>%
  add_osm_feature(key = "highway", 
                  value = c("secondary", "tertiary", "secondary_link", "tertiary_link")) %>%
  osmdata_sf()


small_streets <- getbb("Nashville Tennessee")%>%
  opq()%>%
  add_osm_feature(key = "highway", 
                  value = c("residential", "living_street",
                            "unclassified",
                            "service", "footway"
                  )) %>%
  osmdata_sf()
```

```{r}
# Add other distinctive features to the map, such as rivers and railways.
river <- getbb("Nashville Tennessee")%>%
  opq()%>%
  add_osm_feature(key = "waterway", value = "river") %>%
  osmdata_sf()
```

```{r}
railway <- getbb("Nashville Tennessee")%>%
  opq()%>%
  add_osm_feature(key = "railway", value="rail") %>%
  osmdata_sf()
```

```{r}
# This is just a preview - what does one level of roads look like, with no additional formatting?
ggplot() +
  geom_sf(data = big_streets$osm_lines,
          inherit.aes = FALSE,
          color = "black")
```

```{r}
# Add it all together to create a full map of the city!
# Note that you can use colors and line thickness/weight to distinguish the levels we already created.
ggplot() +
  geom_sf(data = river$osm_lines,
          inherit.aes = FALSE,
          color = "steelblue",
          size = .8,
          alpha = .3) +
  geom_sf(data = railway$osm_lines,
          inherit.aes = FALSE,
          color = "black",
          size = .2,
          linetype="dotdash",
          alpha = .5) +
  geom_sf(data = med_streets$osm_lines,
          inherit.aes = FALSE,
          color = "black",
          size = .3,
          alpha = .5) +
  geom_sf(data = small_streets$osm_lines,
          inherit.aes = FALSE,
          color = "#666666",
          size = .2,
          alpha = .3) +
  geom_sf(data = big_streets$osm_lines,
          inherit.aes = FALSE,
          color = "black",
          size = .5,
          alpha = .6) +
  
  coord_sf(xlim = c(-86.95, -86.62), # Set the borders of your map (influenced the getbb() from above)
           ylim = c(36.03, 36.30),
           expand = FALSE)  +
  
  theme_void() + # get rid of background color, grid lines, etc.
  
  theme(plot.title = element_text(size = 20, face="bold", hjust=.5), # Add a title to your map
        plot.subtitle = element_text(size = 8, hjust=.5, margin=margin(2, 0, 5, 0))) +
  labs(title = "NASHVILLE", subtitle = "36.1627째N / 86.7816째W")
```

```{r}
# Update your map borders to fit within a LinkedIn Header 
# (you'll have to play around with this until you're happy)
ggplot() +
  geom_sf(data = river$osm_lines,
          inherit.aes = FALSE,
          color = "steelblue",
          size = .8,
          alpha = .3) +
  geom_sf(data = railway$osm_lines,
          inherit.aes = FALSE,
          color = "black",
          size = .2,
          linetype="dotdash",
          alpha = .5) +
  geom_sf(data = med_streets$osm_lines,
          inherit.aes = FALSE,
          color = "black",
          size = .3,
          alpha = .5) +
  geom_sf(data = small_streets$osm_lines,
          inherit.aes = FALSE,
          color = "#666666",
          size = .2,
          alpha = .3) +
  geom_sf(data = big_streets$osm_lines,
          inherit.aes = FALSE,
          color = "black",
          size = .5,
          alpha = .6) +
  coord_sf(xlim = c(-86.95, -86.62), 
           ylim = c(36.142, 36.195),
           expand = FALSE)  +
  theme_void() + 
  theme(plot.title = element_text(size = 12, face="bold", hjust=.5),
        plot.subtitle = element_text(size = 6, hjust=.5, margin=margin(2, 0, 5, 0))) +
  labs(title = "NASHVILLE", subtitle = "36.1627째N / 86.7816째W")

ggsave("linkedin_map_header.png", width = 7.29, height = 2.5) # Save image as png
```


That concludes this notebook! Again, check out the original tutorial for more details,
as well as information on how to add some fun details to your map (like highlighting specific
roads or adding a layer of markers for something of interest to you). If you end up using this,
I'd be thrilled if you sent me a message for to check out your handiwork!

-Matt



